Sound Automated Synthesis of Digital Controllers

### 2016-10-08 paper/paper.tex
citation for the design of the digital controller candidate solution + typo

\paragraph{Program synthesis for the running example}
We will illustrate our synthesis approach on the running example 
in Sec.~\ref{sec:running-ex}.
We start with a candidate solution that has all coefficients 0:
%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.

@@

We add this counterexample to {\sc inputs} and initiate the {\sc synthesise} phase, where we get the following candidate solution: 
\red{[ How is the order of the candidate solution chosen here?]}
$$
\begin{array}{ll}
N_C(z) {=} 4.00888156890869140625z^2{-}0.00041961669921875z\\
\qquad\qquad -0.000213623046875\\
D_C(z) {=} -0.003753662109375z^2{+}7.37355804443359375z \\
\qquad\qquad -7.2847900390625\\
\end{array}
$$

>>>>

\paragraph{Program synthesis for the running example}
We will illustrate our synthesis approach on the running example 
in Sec.~\ref{sec:running-ex}.
We start with the candidate solution given below, which has all coefficients 0.
Note that the digital controller is designed with typical control system
techniques \cite{Kuo:2002:ACS:579453,Ogata:1987:DCS:26170}.
%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.

@@

We add this counterexample to {\sc inputs} and initiate the {\sc synthesise} phase, where we get the following candidate solution: 
%\red{[ How is the order of the candidate solution chosen here?]}
$$
\begin{array}{ll}
N_C(z) {=} 4.00888156890869140625z^2{-}0.00041961669921875z\\
\qquad\qquad -0.000213623046875\\
D_C(z) {=} -0.003753662109375z^2{+}7.37355804443359375z \\
\qquad\qquad -7.2847900390625\\
\end{array}
$$
